Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-08-30 talk/talk.tex
Use the white background logo
Reorder
CP Model

        \node (logo) [anchor=north east, shift={(-0.15cm,-0.65cm)}] at (current page.north east) {
            \begin{minipage}{0.25\paperwidth}
                \begin{center}
                \includegraphics*[keepaspectratio=true,scale=0.4]{UoG_keyline.pdf} \\[0.15cm]
                    \colorbox{white}{\includegraphics*[keepaspectratio=true,scale=0.14]{Universite_Lyon_1.pdf}}\\[0.15cm]
                \includegraphics*[keepaspectratio=true,scale=0.12]{Logo_INSALyon-pantone-cartouche.pdf}
                \end{center}
            \end{minipage}
        };

@@

\begin{frame}{CP Models}
\end{frame}

@@

\begin{frame}{Benchmark Instances}
    \begin{itemize}
        \item Standard benchmark suite of 81,000 instances (random with varying densities; 2D, 3D
            and 4D regular and irregular meshes; regular bounded degree graphs, and irregular
            bounded degree graphs).
        \item Labels on vertices and edges:
            \begin{itemize}
                \item Up to 100 vertices.
                \item Number of labels is 33\% of the number of vertices.
            \end{itemize}
        \item Unlabelled:
            \begin{itemize}
                \item Up to 35 vertices.
            \end{itemize}
    \end{itemize}
\end{frame}

>>>>

        \node (logo) [anchor=north east, shift={(-0.15cm,-0.65cm)}] at (current page.north east) {
            \begin{minipage}{0.25\paperwidth}
                \begin{center}
                \includegraphics*[keepaspectratio=true,scale=0.45]{UoG_colour.pdf} \\[0.15cm]
                    \colorbox{white}{\includegraphics*[keepaspectratio=true,scale=0.14]{Universite_Lyon_1.pdf}}\\[0.15cm]
                \includegraphics*[keepaspectratio=true,scale=0.12]{Logo_INSALyon-pantone-cartouche.pdf}
                \end{center}
            \end{minipage}
        };

@@

\begin{frame}{CP Models}
    \begin{itemize}
        \item One variable for each vertex in the smaller input graph.
        \item Domains range over vertices in the other input graph, plus $\bot$.
        \item Objective is to maximise variables not assigned $\bot$.
        \item Adjacent pairs of non-$\bot$ vertices must be mapped to adjacent pairs of vertices.
        \item Non-adjacent pairs of non-$\bot$ vertices must be mapped to non-adjacent pairs of vertices.
        \item All different except $\bot$, with number of allowed $\bot$ occurrences controlled by
            the objective variable.
        \item Smallest domain first, prefer vertices of similar degree.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Benchmark Instances}
    \begin{itemize}
        \item Standard benchmark suite of 81,000 instances (random with varying densities; 2D, 3D
            and 4D regular and irregular meshes; regular bounded degree graphs, and irregular
            bounded degree graphs).
        \item Unlabelled:
            \begin{itemize}
                \item Up to 35 vertices.
            \end{itemize}
        \item Labels on vertices and edges:
            \begin{itemize}
                \item Up to 100 vertices.
                \item Number of labels is 33\% of the number of vertices.
            \end{itemize}
    \end{itemize}
\end{frame}
